---
title: Understanding the patterns of global re-emergence of RSV following COVID19 pandemic
author: "Deus & Dan"
date: "01/12/2022"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{=html}
<style type="text/css">
.main-container {
  max-width: 1300px;
  margin-left: auto;
  margin-right: auto;
}
</style>
```

&nbsp;

### Load required packages for entire project

```{r LoadPackages, results = 'hide', message = FALSE, warning = FALSE}
library(here)
source(here("script", "01_mainRSV.R"))
                        
```

&nbsp;

### Run the archiving script to update the RSV dataset

```{r RunFileCache, results = "hide", message = FALSE, warning = FALSE}

source(here("script", "02_fileCache.R"))
source(here("script", "03_runIfExpired.R"))

```

&nbsp;

### Load RSV datasets for OTher countries 

```{r LoadRSVdataOT, results = "hide", message = FALSE, warning = FALSE}

source(here("script", "04_loadRSVdata_OT.R"))

```

&nbsp;

### Load RSV datasets for the US

```{r LoadRSVdataUS, results = "hide", message = FALSE, warning = FALSE}

source(here("script", "04_loadRSVdata_US.R"))

```

&nbsp;

### Seasonal dynamics of RSV by WHO region

```{r PlotRSV1, message = FALSE, warning = FALSE, fig.width = 16, fig.height = 8, fig.align = 'center'}

source(here("script", "05_seasRSV_region.R"))

```

&nbsp;

### Seasonal dynamics of RSV by Hemisphere

```{r PlotRSV2, message = FALSE, warning = FALSE, fig.width = 12, fig.height = 5, fig.align = 'center'}

source(here("script", "06_seasRSV_hemi.R"))

```

&nbsp;

### Dynamics of RSV in African countries

```{r PlotRSV3, message = FALSE, warning = FALSE, fig.width = 12, fig.height = 8, fig.align = 'center'}

source(here("script", "07_seasRSV_afr.R"))

```

&nbsp;

### Dynamics of RSV in South East Asian countries

```{r PlotRSV4, message = FALSE, warning = FALSE, fig.width = 16, fig.height = 6, fig.align = 'center'}

source(here("script", "08_seasRSV_sear.R"))

```

&nbsp;

### Dynamics of RSV in Western Pacific countries

```{r PlotRSV5, message = FALSE, warning = FALSE, fig.width = 16, fig.height = 8, fig.align = 'center'}

source(here("script", "09_seasRSV_wpr.R"))

```

&nbsp;

### Dynamics of RSV in Eastern Mediterranean countries

```{r PlotRSV6, message = FALSE, warning = FALSE, fig.width = 16, fig.height = 6, fig.align = 'center'}

source(here("script", "10_seasRSV_emr.R"))

```

&nbsp;

### Dynamics of RSV in European countries

```{r PlotRSV7, message = FALSE, warning = FALSE, fig.width = 16, fig.height = 12, fig.align = 'center'}

source(here("script", "11_seasRSV_eur.R"))

```

&nbsp;

### Dynamics of RSV in Americas countries

```{r PlotRSV8, message = FALSE, warning = FALSE, fig.width = 16, fig.height = 14, fig.align = 'center'}

source(here("script", "12_seasRSV_amr.R"))

```

### Dynamics of RSV in the United States of America

```{r PlotRSV9, message = FALSE, warning = FALSE, fig.width = 16, fig.height = 8, fig.align = 'center'}

source(here("script", "13_seasRSV_usa.R"))

```
